Fusing Filters with Integer Linear Programming

### 2014-05-04 2014betterfusionforfilters/section/03-SizeInference.tex
Shift size inference constraints to new file
Another go at size inference constraint generation
add generate to constrs

The final clauses show how the constraint holes are filled by constraints of subsequent bindings. If there no bindings, the constraint is trivially true.

@@

@@

\begin{tabbing}
MMMMM       \= MM \= MMMMMMMMMMM \= \kill
$\tau$       \> @::=@ \> $size$                                  \> (known size) \\
             \> $~|$  \> @external@                              \> (external and unfusible) \\
\end{tabbing}

@@

\begin{tabbing}
MM \= MM \= MMMMMMMMM \= MMMM \= MM \= \kill
$\tau$  \>$::$\> $binds \rightarrow name \rightarrow \tau$ \\
\\
$\tau_{bs,o}$    
            \> $|$ \> $o = @fold@~f~n$      \> $\in bs$ \> $=$ \> $k_n$ \\
            \> $|$ \> $o = @map@_n~f~ns$    \> $\in bs$ \> $=$ \> $k_o$ \\
            \> $|$ \> $o = @filter@~f~n$    \> $\in bs$ \> $=$ \> $k_n$ \\
            \> $|$ \> $o = @gather@~i~d$    \> $\in bs$ \> $=$ \> $k_i$ \\
            \> $|$ \> $o = @cross@~a~b$     \> $\in bs$ \> $=$ \> $k_a \times k_b$ \\
            \> $|$ \> $o = @external@~ins$  \> $\in bs$ \> $=$ \> $@external@$ \\
\end{tabbing}

@@

\begin{tabbing}
MMM       \= MM \= MMMMMM \= MM \= MMM \= MM \= \kill
$gen$   \> @::@  \> $\{constraint\}$  \> $\to$ \> $array$ \> $\to$ \> $\{array\}$ \\
MMMMMMM                 \= M  \= MMMMMMMM \= MM \= \kill
$gen(constrs, a)$ \> $|$ \> $a \le_c b \in constrs$ \> $=$ \> $\{b\}$                        \\
$gen(constrs, a)$ \> $|$ \> $a =_c b \in constrs$   \> $=$ \> $\bigcup gen(constrs, b)$                        \\
$gen(constrs, a)$ \> $|$ \> $otherwise$             \> $=$ \> $\emptyset$                        \\
\end{tabbing}

%\begin{lemma}
\textbf{Lemma: unique generation of filters}
For some bindings $bs$ and associated constraints $cs$, then
\[
valid(cs) \implies \forall x. (\exists y \in bs. gen(cs, x) = \{y\}) \vee gen(cs, x) = \emptyset
\]
%\end{lemma}

>>>>

The final clauses show how the constraint holes are filled by constraints of subsequent bindings. If there are no bindings, the constraint is trivially true.

@@

\constr{u_o &=& @generate@~ s~ f;~ bs}
        & = &   \forall u_o^k.\ \constr{bs}
\\[0.5ex]

@@

\begin{tabbing}
MMMMM       \= MM \= MMMMMMMMMMM \= \kill
$T$          \> @::=@ \> $size$                                  \> (known size) \\
             \> $~|$  \> @external@                              \> (external and unfusible) \\
\end{tabbing}

@@

\begin{tabbing}
MM \= MM \= MMMMMMMMM \= MMMM \= MM \= \kill
$\tau$  \>$::$\> $binds \rightarrow name \rightarrow T$ \\
\\
$\tau_{bs,o}$    
            \> $|$ \> $o = @fold@~f~n$      \> $\in bs$ \> $=$ \> $k_n$ \\
            \> $|$ \> $o = @map@_n~f~ns$    \> $\in bs$ \> $=$ \> $k_o$ \\
            \> $|$ \> $o = @filter@~f~n$    \> $\in bs$ \> $=$ \> $k_n$ \\
            \> $|$ \> $o = @generate@~s~f$  \> $\in bs$ \> $=$ \> $k_o$ \\
            \> $|$ \> $o = @gather@~i~d$    \> $\in bs$ \> $=$ \> $k_i$ \\
            \> $|$ \> $o = @cross@~a~b$     \> $\in bs$ \> $=$ \> $k_a \times k_b$ \\
            \> $|$ \> $o = @external@~ins$  \> $\in bs$ \> $=$ \> $@external@$ \\
\end{tabbing}

@@

\begin{tabbing}
MM \= MM \= MMMMMMMMM \= MMMM \= MM \= \kill
$gen$  \>$::$\> $binds \rightarrow name \rightarrow \{name\}$ \\
$gen(bs,o)$    \\
            \> $|$ \> $o = @fold@~f~n$      \> $\in bs$ \> $=$ \> $\emptyset$ \\
            \> $|$ \> $o = @map@_n~f~ns$    \> $\in bs$ \> $=$ \> $\bigcup_{n \in ns} gen(bs, n)$ \\
            \> $|$ \> $o = @filter@~f~n$    \> $\in bs$ \> $=$ \> $\{o\}$       \\
            \> $|$ \> $o = @generate@~s~f$  \> $\in bs$ \> $=$ \> $\emptyset$ \\
            \> $|$ \> $o = @gather@~i~d$    \> $\in bs$ \> $=$ \> $gen(bs,i)$ \\
            \> $|$ \> $o = @cross@~a~b$     \> $\in bs$ \> $=$ \> $\emptyset$ \\
            \> $|$ \> $o = @external@~ins$  \> $\in bs$ \> $=$ \> $\emptyset$ \\
\end{tabbing}

%\begin{lemma}
\textbf{Lemma: unique generators}
For some bindings $bs$, then
\[
valid(\constr{bs}) \implies \forall x.\ |gen(bs, x)| \le 1
\]
%\end{lemma}
